Supplementary Information for:

### 2017-07-11 supp/supp.Rmd
load coRal library

```{r setup, include=FALSE}
require(pander)
require(stringr)
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(message = F, warning = F, echo=T, results='asis')
knitr::opts_chunk$set(results = "asis", render=pander)
```

```{r initialize, include=FALSE}
# Source default parameters and functions
sapply(c("R/run_steady_states.R", "R/plot_steady_states.R", "R/reported_metrics.R",
         "R/sensitivity.R", "R/conversions.R"), source, .GlobalEnv)
# Get default parameters
defpars <- def_pars()
```

@@

# Run simulations
ss1 <- with(run_coral_ss(env=list(L=32,N=0.14e-6,X=1e-6), pars=defpars, dt=0.1), last(S$S/H$H))
run1 <- run_coral(time=time, env=env1, pars=replace(defpars, "initS", ss1))
ss2 <- with(run_coral_ss(env=list(L=32,N=15.14e-6,X=1e-6), pars=defpars, dt=0.1), last(S$S/H$H))
run2 <- run_coral(time=time, env=env2, pars=replace(defpars, "initS", ss2))

>>>>

```{r setup, include=FALSE}
require(pander)
require(stringr)
require(coRal)
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(message = F, warning = F, echo=T, results='asis')
knitr::opts_chunk$set(results = "asis", render=pander)
```

```{r initialize, include=FALSE}
# Source default parameters and functions
sapply(c("R/run_steady_states.R", "R/plot_steady_states.R", "R/reported_metrics.R",
         "R/sensitivity.R", "R/conversions.R"), source, .GlobalEnv)
# Get default parameters
defpars <- coRal::def_pars()
```

@@

# Run simulations
ss1 <- with(coRal::run_coral_ss(env=list(L=32,N=0.14e-6,X=1e-6), pars=defpars, dt=0.1), dplyr::last(S$S/H$H))
run1 <- coRal::run_coral(time=time, env=env1, pars=replace(defpars, "initS", ss1))
ss2 <- with(coRal::run_coral_ss(env=list(L=32,N=15.14e-6,X=1e-6), pars=defpars, dt=0.1), dplyr::last(S$S/H$H))
run2 <- coRal::run_coral(time=time, env=env2, pars=replace(defpars, "initS", ss2))
